### 2014-08-02 paper/paper.tex
Removed the old huge table

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
        \hline
                   & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
        \hline
        \textit{a} & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
        \textit{b} & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
        \textit{c} & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
        \textit{d} & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
        \textit{e} & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
        \textit{f} & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
        \textit{g} & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
        \textit{h} & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
        \textit{i} & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
        \textit{j} & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
        \textit{k} & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
        \textit{l} & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
        \textit{m} & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
        \textit{n} & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
        \textit{o} & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
        \textit{p} & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. The
    `Citation' column indicates what type of classifier is being used. The
    `Stopwords' column indicates if stop words have been removed. The `Uncommon'
    column indicates if words with a document frequency lower than the threshold
    (in this case more than one occurrence) have been removed. The `Normalize'
    column indicates if the any steps have been taken to normalize features.}
    \label{table:results}
\end{table}

>>>>

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F  \\
        \hline
           All            & 0.0   & 0.0    \\
           Just Stopwords & 0.0    & 0.0    \\
           Just Uncommon  & 0.0    & 0.0    \\
           Just Normalize & 0.0    & 0.0    \\
           Baseline       & 0.0    & 0.0    \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Holla!}
    \label{table:results}
\end{table}

\begin{figure}[H]
    \includegraphics{figures/maxent_boxplot.png}
    \caption{Caption...}
    \label{figure:maxent}
\end{figure}
